Two Mode Networks and Relational Similarity

### 2023-09-01 analysis.qmd
New plots based on updated function

# Analysis
```{r Reflections Bump Charts}
   evens <- function(x) subset(x, x %% 2 == 0)
   odds <- function(x) subset(x, x %% 2 != 0)
   a <- reflections(A, iter = 26)
   p.e.r <- a$p.r[, evens(1:20)]
   p.o.r <- a$p.r[, odds(1:20)]
   p.o.r <- p.o.r[, -1]
   b <- ref.long.dat(a = a$p.r, b = a$g.r, max.iter = 26)
   plot.dat <- b$person$even
   p <- ggplot(data = filter(plot.dat, n.iter < 22),
               mapping = aes(x = n.iter, y = ref, color = person))
   # geoms
   p <- p + geom_bump(linewidth = 1, smooth = 8, alpha = 0.4)
   p <- p + geom_point(size = 4, alpha = 0.8)
   p <- p + geom_text_repel(data = filter(plot.dat, n.iter == 2), 
                                    aes(x = n.iter, label = person), 
                                    size = 4, nudge_x = -3)
   p <-    p <- p + geom_text(data = filter(plot.dat, n.iter == 22), 
                              aes(x = n.iter, label = person), 
                              size = 4, nudge_x = 0.5)

@@

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A)
   b <- a$A.plot.ca
   c <- a$A.plot.bon
   png(file = here("Plots", "ca-v-bon-reord.png"), width=1000, height=700)
      (b | c) + plot_annotation(tag_levels = "a")
   dev.off() 
```

```{r}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 6, d.r = 6, d.c = 6, b.r = 4, b.c = 4)
    a <- tmCA.res$bon.sim.plot.r + theme(axis.text.x = element_blank())
    b <- tmCA.res$bon.sim.plot.c + theme(axis.text.x = element_blank())
    c <- tmCA.res$bon.corr.plot

    png(file = here("Plots", "bon-sim.png"), width=950, height=700)
        (a | b) / c + plot_annotation(tag_levels = "a")
    dev.off() 
```

@@

    png(file = here("Plots", "eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a")
    dev.off()

    png(file = here("Plots", "sim.png"), width=950, height=700)
        (e | f) / g + plot_annotation(tag_levels = "a")
    dev.off() 
```

>>>>

# Analysis

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A, k.r = 5)

```

```{r Reflections Bump Charts}
   evens <- function(x) subset(x, x %% 2 == 0)
   odds <- function(x) subset(x, x %% 2 != 0)
   a <- reflections(A, iter = 26)
   p.e.r <- a$p.r[, evens(1:20)]
   p.o.r <- a$p.r[, odds(1:20)]
   p.o.r <- p.o.r[, -1]
   b <- ref.long.dat(a = a$p.r, b = a$g.r, max.iter = 26)
   plot.dat <- b$person$even
   p <- ggplot(data = filter(plot.dat, n.iter < 22),
               mapping = aes(x = n.iter, y = ref, color = person))
   # geoms
   p <- p + geom_bump(linewidth = 1, smooth = 8, alpha = 0.4)
   p <- p + geom_point(size = 4, alpha = 0.8)
   p <- p + geom_text_repel(data = filter(plot.dat, n.iter == 2), 
                                    aes(x = n.iter, label = person), 
                                    size = 4, nudge_x = -3)
   p <-    p <- p + geom_text(data = filter(plot.dat, n.iter == 22), 
                              aes(x = n.iter, label = person), 
                              size = 4, nudge_x = 0.5)

@@

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A)
   b <- a$A.plot.ca
   c <- a$A.plot.bon
   png(file = here("Plots", "ca-v-bon-reord.png"), width=1000, height=700)
      (b | c) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
   dev.off() 
```

```{r Similarity and Correspondence Plot (Bonacich)}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 6, d.r = 6, d.c = 6, b.r = 4, b.c = 4)
    a <- tmCA.res$bon.sim.plot.r + theme(axis.text.x = element_blank())
    b <- tmCA.res$bon.sim.plot.c + theme(axis.text.x = element_blank())
    c <- tmCA.res$bon.corr.plot

    png(file = here("Plots", "bon-sim.png"), width=950, height=700)
      (a | b) / c + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20)) 
    dev.off() 
```

@@

    png(file = here("Plots", "eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off()

    png(file = here("Plots", "sim.png"), width=950, height=700)
        (e | f) / g + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off() 
```
